Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-10 edubots_surveys.Rnw
adds author and fixes title refs #8
fixes typos in abstract refs #5

%%% Begin ...
\begin{document}

@@

\title{Chatbots in the classroom: a analysis from the teacher's perspective}

@@

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}

@@

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but, above all, an examination of the attitudes of the affected community. In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms, what are their needs, what kind of use case they see for them, and in what kind of environment they think its use will be useful. We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.
\end{abstract}

>>>>

%%% Begin ...
\begin{document}
\SweaveOpts{concordance=TRUE}

@@

\title{Chatbots in the classroom: an analysis from the teacher's perspective}

@@

\author[
  addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
  corref={aff1},                       % id of corresponding address, if any
  email={jmerelo@ugr.es}   % email address
]{\inits{J.J.}\fnm{Juan J.} \snm{Merelo}}
\author[
  addressref={aff1},
  email={pacv@ugr.es}   % email address
]{\inits{P.A.}\fnm{Pedro A.} \snm{Castillo}}
\author[
  addressref={aff2},
  email={amorag@ugr.es}
]{\inits{A.M.G}\fnm{Antonio M.} \snm{Mora}}
\author[
  addressref={aff1},
  email={fbarranco@ugr.es}
]{\inits{F.}\fnm{Francisco} \snm{Barranco}}

@@

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community. In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think of the introduction of messaging platforms, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable. We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching.
\end{abstract}
